A Convolutional Neural Network for Outsole Recognition\tnoteref{t1}

### 2019-07-01 paper/paper.Rnw
doubleblind mode

\documentclass[review]{elsarticle}

@@

%% Group authors per affiliation:
\author{Miranda Tilton and Susan Vanderplas\fnref{csafe}}
\address{Center for Statistical Applications in Forensic Evidence, Iowa State University}
\fntext[csafe]{195 Durham Center, 613 Morill Rd., Ames, IA 50011.}

>>>>

\documentclass[doubleblind,review]{elsarticle}

@@

%% Group authors per affiliation:
\author{Miranda Tilton and Susan Vanderplas}
\address{Center for Statistical Applications in Forensic Evidence, Iowa State University. 195 Durham Center, 613 Morill Rd., Ames, IA 50011}
